---
title: "02-Assignment"
output: github_document
---

For this assignment, you'll be working with the `sc_debt.Rds` to predict earnings levels of college graduates using conditional means. You'll need to select the college-level characteristics that you think might be related to earnings levels. Please complete the following steps:

```{r}
library(tidyverse)
library(yardstick)
```

```{r}
sc<-readRDS("sc_debt.Rds")
```


1. Calculate the mean of the outcome `md_earn_wne_p6`

```{r}
sc%>%summarize(mean_earnings=mean(md_earn_wne_p6,na.rm=TRUE))
```


2. Use your mean as a prediction: Create a new variable that consists of the mean of the outcome.

```{r}
sc<-sc%>%
  mutate(mean_earnings=mean(md_earn_wne_p6,na.rm=TRUE))

```


3. Calculate a summary measure of the errors for each observation---the difference between your prediction and the outcome.

```{r}
sc%>%rmse(md_earn_wne_p6,mean_earnings)
```


4. Calculate the mean of the outcome at levels of a predictor variable. 

```{r}
sc%>%
  group_by(region)%>%
  summarize(mean_earnings_region=mean(md_earn_wne_p6,na.rm=TRUE))%>%
  arrange(-mean_earnings_region)
```


5. Use these conditional means as a prediction: for every college, use the conditional mean to provide a ''best guess'' as to that college's level of the outcome.  

```{r}
sc<-sc%>%
  group_by(region)%>%
  mutate(mean_earnings_region=mean(md_earn_wne_p6,na.rm=TRUE))%>%
  ungroup()

```


6. Calculate a summary measure of the error in your predictions.
```{r}
sc%>%rmse(md_earn_wne_p6,mean_earnings_region)
```


```{r}
sc%>%
  ggplot(aes(x=fct_reorder(region,mean_earnings_region),y=md_earn_wne_p6))+
  geom_point(size=.5,alpha=.5)+
  geom_point(aes(x=region,y=mean_earnings_region),color="blue")
```


7. Repeat the above process using the tool of conditional means, try to find 3-4 combined variables that predict the outcome with better (closer to 0) summary measures of error. Report the summary measures of error and the variables (as text in your `.Rmd` file).

```{r}
sc%>%
  mutate(sat_level=ntile(sat_avg,4))%>%
  group_by(sat_level)%>%
  summarize(mean_sat=mean(md_earn_wne_p6,na.rm=TRUE),count=n())

sc%>%
  group_by(region)%>%
  summarize(count=n())

```

```{r}
sc<-sc%>%
  mutate(sat_level=ntile(sat_avg,4))%>%
  group_by(region,control,preddeg,sat_level)%>%
  mutate(mean_earnings_lots_of_predictors=mean(md_earn_wne_p6,na.rm=TRUE))%>%
  ungroup()

sc%>%rmse(md_earn_wne_p6,mean_earnings_lots_of_predictors)

```



Submit your assignment as `02-assignment-<yourlastname>.Rmd`, where `<yourlastname>` is your last name. (By the way, any time you see this: `<sometext>`, that indicates that you need to substitute something in, so if I were to submit the above assignment, it would be as: `02-assignment-doyle.Rmd`)

I expect that the `.Rmd` file you submit will run cleanly, and that there shouldn't be any errors. Use LOTS of text to tell me what you are doing. 