---
title: 'Conditional Means: In Class'
author: "Will Doyle"
date: "5/19/2021"
output: html_document
---

```{r}
library(tidyverse)
library(yardstick)
```


```{r}
load("caschool.rdata")
```

The California School data has the following elements

| Name  | Description  |
|---|---|
| id   | School Id  |
| stype  | School Type (E=elem, M=middle, H=HS)  |
| sname  | School Name   |
| dname  | District Name   |
| cname  |  County Name |
| api  | Academic Performance Index Score   |
| yr_rnd  | Year Round School? (No/Yes)   |
| acs_k3  | Average Class Size K-3   |
| acs_46   | Average Class Size 4-6   |
| chartr   | Charter (1=yes,0=no)  |



1. Calculate the mean of api scores for all schools

```{r}
ca%>%summarize(mean_api=mean(api,na.rm=TRUE))
```

```{r}
mean(ca$api,na.rm=TRUE)
```



2. Calculate the conditional mean of api scores by school type

```{r}
ca%>%
  group_by(stype)%>%
  summarize(mean_api=mean(api,na.rm=TRUE))
```


3. Calculate the root mean squared error if school type is used to predict api scores. What does this tell you?

```{r}
ca<-ca%>%
   group_by(stype)%>%
  mutate(mean_api=mean(api,na.rm=TRUE))%>%
  ungroup()

ca%>%rmse(api,mean_api)
```



4. Calculate the conditional mean of api scores by school type and another variable. 

```{r}
ca%>%
   group_by(stype,chartr)%>%
   summarize(mean_api=mean(api,na.rm=TRUE))
```


5. Calculate the root mean squared error of your prediction when using two variables. 

```{r}
ca<-ca%>%
   group_by(stype,chartr)%>%
  mutate(mean_api=mean(api,na.rm=TRUE))%>%
  ungroup()

ca%>%rmse(api,mean_api)
```




```{r}
ca%>%
  filter(stype=="E")%>%
  mutate(class_size_level=ntile(acs_k3,4))%>%
  group_by(class_size_level)%>%
  summarize(mean_api=mean(api,na.rm=TRUE))

ca_elem<-ca%>%
  filter(stype=="E")%>%
  mutate(class_size_level=ntile(acs_k3,4))%>%
  group_by(class_size_level)%>%
  mutate(mean_api=mean(api,na.rm=TRUE))%>%
  ungroup()

ca_elem%>%select(class_size_level,mean_api,api)

ca_elem%>%rmse(api,mean_api)


```

