---
title: 'Conditional Means: In Class'
author: "Will Doyle"
date: "5/19/2021"
output: html_document
---

```{r}
library(tidyverse)
```


```{r}
load("caschool.rdata")
```

The California School data has the following elements

| Name  | Description  |
|---|---|
| id   | School Id  |
| stype  | School Type (E=elem, M=middle, H=HS)  |
| sname  | School Name   |
| dname  | District Name   |
| cname  |  County Name |
| api  | Academic Performance Index Score   |
| yr_rnd  | Year Round School? (No/Yes)   |
| acs_k3  | Average Class Size K-3   |
| acs_46   | Average Class Size 4-6   |
| chartr   | Charter (1=yes,0=no)  |


1. Calculate the mean of api scores for all schools

2. Calculate the conditional mean of api scores by school type

3. Calculate the root mean squared error if school type is used to predict api scores. What does this tell you?

4. Calculate the conditional mean of api scores by school type and another variable. 

5. Calculate the root mean squared error of your prediction when using two variables. 
