---
title: "Assignment 3"
output: github_document
---

Use the `sc_debt.Rds` dataset to answer the following questions. As always, your assignment must be turned in as a .Rmd file. 


```{r}
library(tidyverse)
```

```{r}
df<-readRDS("sc_debt.Rds")
```


1. Create a graph that shows the distribution of grads' income `md_earn_wne_p6`

```{r}

## Option 1: histogram
df%>%
  ggplot(aes(x=md_earn_wne_p6))+
  geom_histogram(fill="lightblue")+
  xlab("Median Earnings")+ylab("Count")+
  theme_minimal()

## Option 2: density plot
df%>%
  ggplot(aes(x=md_earn_wne_p6))+
  geom_density()

```

```{r}
df<-df%>%
  mutate(region=ifelse(region=="Soutwest","Southeast",region))
```



2. Create a graph that shows the average level of income by region.

```{r}
df_sum<-df%>%
  group_by(region)%>%
  summarize(mean_income=mean(md_earn_wne_p6,na.rm=TRUE))

df_sum%>%
  ggplot(aes(x=fct_reorder(region,mean_income),y=mean_income,fill=mean_income))+
  geom_bar(stat="identity")+
  xlab("")+ylab("Mean Income")+
  coord_flip()+
  theme(legend.position = "none")
```


3. Create another graph that shows average level of income by region and selectivity. 


```{r}
df_sum<-df%>%
  mutate(selective=ifelse(selective==1,"Selective","Not Selective"))%>%
  mutate(selective=ifelse(is.na(selective),"Not Selective",selective))%>%
  group_by(region,selective)%>%
  summarize(mean_income=mean(md_earn_wne_p6,na.rm=TRUE))

df_sum%>%
  ggplot(aes(x=fct_reorder(region,mean_income),y=mean_income,fill=selective))+
  geom_bar(stat="identity",position="dodge")+
  xlab("")+ylab("Mean Income")+
  coord_flip()+
  theme(legend.position = "none")+
  theme_minimal()
```


4. Create a graph that shows average levels of income by region, selectivity, and predominant degree. 


```{r}
df_sum<-df%>%
  mutate(selective=ifelse(selective==1,"Selective","Not Selective"))%>%
  mutate(selective=ifelse(is.na(selective),"Not Selective",selective))%>%
  group_by(region,selective,preddeg)%>%
  summarize(mean_income=mean(md_earn_wne_p6,na.rm=TRUE))

df_sum%>%
  ggplot(aes(x=fct_reorder(region,mean_income),y=mean_income,fill=selective))+
  geom_bar(stat="identity",position="dodge")+
  xlab("")+ylab("Mean Income")+
  coord_flip()+
  theme(legend.position = "none")+
  facet_wrap(~preddeg)+
  theme_minimal()
```


5. Create a graph that shows average levels of income by region, selectivity, and predominant degree and control. 

```{r}
df_sum<-df%>%
  mutate(selective=ifelse(selective==1,"Selective","Not Selective"))%>%
  mutate(selective=ifelse(is.na(selective),"Not Selective",selective))%>%
  group_by(region,selective,preddeg,control)%>%
  summarize(mean_income=mean(md_earn_wne_p6,na.rm=TRUE))

df_sum%>%
  ggplot(aes(x=fct_reorder(region,mean_income),y=mean_income,fill=selective))+
  geom_bar(stat="identity",position="dodge")+
  xlab("")+ylab("Mean Income")+
  coord_flip()+
  theme(legend.position = "none")+
  facet_wrap(control~preddeg)+
  theme_minimal()
```
