---
title: "03-plot-means-inclass.Rmd"
author: "Doyle"
date: "2/11/2021"
output: github_document
---

```{r}
library(tidyverse)
library(RColorBrewer)
```

```{r}
df<-readRDS("sc_debt.Rds")
```


## Plotting Means: In Class Work

1. Using the student debt dataset, calculate and plot average SAT by region. Plot the result using a bar plot. Make it nicely labeled and beautiful in every way.

```{r}


df_sum<-sc%>%
  group_by(region)%>%
  summarize(mean_sat=mean(sat_avg,na.rm=TRUE))

df_sum%>%
  ggplot(aes(x=fct_reorder(region,mean_sat),y=mean_sat))+
  geom_bar(stat = "identity",fill="lightblue")+
  xlab("Region")+ylab("Mean SAT Scores")


```


2. Repeat the above plot, but use a dot plot and reverse the axes. 


```{r}

df_sum%>%
  ggplot(aes(x=fct_reorder(region,mean_sat),y=mean_sat))+
  geom_point()+
  xlab("Region")+ylab("Mean SAT Scores")+
  coord_flip()

```



3. Calculate and plot average SAT scores  by region  AND predominant degree type. Use a bar plot. 


```{r}

df_sum<-sc%>%
  group_by(region,preddeg)%>%
  summarize(mean_sat=mean(sat_avg,na.rm=TRUE))

df_sum%>%
  ggplot(aes(x=fct_reorder(region,mean_sat),y=mean_sat,fill=preddeg))+
  geom_bar(stat="identity",position="dodge")+
  ylab("Earnings")+xlab("Region")

  

```


4. Change the color scheme of the above plot. 

Using RColorBrewer
```{r}

```



```{r}

```


5. Calculate and plot SAT scores by region and predominant degree with a separate plot (hint:facet_wrap) for public and private institutions.  
```{r}

```




