Assignment 5
----------------


```{r,echo=FALSE}
library(tidyverse)
library(tidymodels)
library(plotly)
```


```{r}
ad<-readRDS("area_data.Rds")
```

1. Run a model on a training subset of the data which predicts the percent of the population in the labor force (dependent variable) as a function of the percent of the population that is insured (independent variable). 

2. Summarize the coefficient for percent of the population that is insured in a sentence or two. 

3. Calculate the model fit by calculating the rmse in the *testing* data. 

4. Add variables for the census division and the percent of the population with incomes above 30 minutes. Comment on the estimates for both of these variables. (*N.B: the census division is a categorical variable* ). 

5. Calculate the model fit by examining the rmse in the testing data. Comment in a sentence on what the rmse means and how it compares to the rmese in step 3. 

6. Create another model by adding at least two other variables. Answer the following questions in a sentence for each:
  - What is the rmse from your new model? How does it compare to the rmse from the previous model? 
  - Which predictors appear to be related to the outcome? How do you know?

