---
title: Regression, Part 2
author: Will Doyle
output: html_document
---

## Introduction

In this section we're going to continue fitting regression to the training data and
testing the predictions against the testing data. We're also going to add some new elements.
We'll be using independent variables or predictor variables that are binary or categorical. In addition, we'll start using `workflows` that put the various steps of our modeling workflow together. 

We'll need the same libraries as last week:

```{r}
library(tidyverse)
library(tidymodels)
library(plotly)
```


And the same dataset, which includes data on a variety of metropolitan and micropolitan areas in the United States. 

```{r}
ad<-readRDS("area_data.Rds")
```


## Training and Testing Data

As before, I'm going to split the data into training and testing versions. 

```{r}
set.seed(35202)


split_data<-ad%>%initial_split(prop=.5)

ad_train<-training(split_data)

ad_test<-testing(split_data)
```

## Set Model

We're going to use the same linear model as last time, so I'll specify that here. 

```{r}
lm_fit <- 
  linear_reg() %>% 
  set_engine("lm")%>%
  set_mode("regression")
```



## Begin Workflow

Now I start my workflow. A workflow is pretty much what it sounds like. It's a set of steps in a modeling process. Right now, it just contains the model. 

```{r}
income_wf<-workflow()%>%
  add_model(lm_fit)
```


## Regression with a binary variable

The next variable I want to include is `metro`, which is a binary variable set to "Yes" if the area is a metropolitan area and "No" if it is not a metropolitan area. The code below shows the number of metropolitan and non-metropolitan areas in the dataset. 

```{r}
ad%>%
  group_by(metro)%>%
  summarise("Number of Areas"=n())%>%
  mutate(`Proportion`=`Number of Areas`/sum(`Number of Areas`))
```

This shows that about 58% of areas are not metro areas, while 42% are metro areas. 

## Set Formula

Next, I add the variable `metro` to the formula. 

```{r}
income_formula<-as.formula("income_75~college_educ+perc_homeown+metro")
```

The variable `metro` is now added to our formula. But we need to tell the model how to handle this variable, since it is a binary variable. 

## Set Recipe
```{r}
income_rec<-recipe(income_formula,data=ad)%>%
  step_dummy(metro)
```

The `recipe` function allows us to get the data ready for analysis, a step that is called [pre-processing](https://towardsdatascience.com/data-preprocessing-concepts-fa946d11c825). In the code above, I create a recipe from the formula and the dataset, then add a pre-processing step, `step_dummy`. This tells R that I want the metro variable to be understood as 0/1 variable. 

## Add recipe to workflow

We can now add the recipe to the previously existing workflow. 

```{r}
income_wf<-income_wf%>%
  add_recipe(income_rec)
```

## Fit to training data

Now we can fit the processed data to the training dataset and take a look at the results. 

```{r}
lm_results<-fit(income_wf,ad_train)

tidy(lm_results)
```

The `tidy` command allows us to see the coefficients from the model fit to the training data. 

The results show that the percent of individuals with incomes about $75,000 is `r tidy(lm_results)[4,2]` higher in metro areas than non-metro areas. This is really important: we always interpret binary variables as a comparison between the group that is set to 1 (metropolitan areas in this case) and the group that is set to 0 (non-metropolitan areas). 

## Predict on testing data and calculate rmse

We can add predictions to the testing dataset in the same way we did before. 

```{r}
ad_test<-
  predict(lm_results,ad_test)%>%
  rename(pred1=.pred)%>%
  bind_cols(ad_test)
```

## Calculate RMSE

Calculating rmse works the same as well. 

```{r}
rmse_1<-ad_test%>%rmse(truth=income_75,estimate=pred1)  
rmse_1
```

So, what we've done at this point is to include a new kind of predictor-- a binary variable-- and include it in a workflow that has both pre-processing and model fitting. 

## Regression with a categorical variable

We can also include caegorical variables in our model using much the same process. 

## Set Formula
```{r}
income_formula<-as.formula("income_75~college_educ+perc_homeown+metro+region")
```



## Begin Workflow

```{r}
income_wf<-workflow()%>%
  add_model(lm_fit)
```


## Set Formula
```{r}
income_formula<-as.formula("income_75~college_educ+perc_homeown+metro+region")
```

## Set Recipe
```{r}
income_rec<-recipe(income_formula,data=ad)%>%
  step_dummy(metro,region)
```

## Add recipe to workflow
```{r}
income_wf<-income_wf%>%
  add_recipe(income_rec)
```


## Fit to training data and look at coefficients and model fit
```{r}
lm_results<-fit(income_wf,ad_train)

tidy(lm_results)

pull_workflow_fit(lm_results)
```


## Predict on testing data and calculate rmse
```{r}
ad_test<-
  predict(lm_results,ad_test)%>%
  rename(pred2=.pred)%>%
  bind_cols(ad_test)
```

## Calculate RMSE
```{r}
rmse_2<-ad_test%>%rmse(truth=income_75,estimate=pred2)  
rmse_2
```

## Or get there the easy way
```{r}
lf<-last_fit(income_wf,split=split_data)
lf$.metrics
```

