---
title: "Regression: In Class Work"
author: "Will Doyle"
---

```{r}
library(tidyverse)
library(tidymodels)
library(plotly)
```

```{r}
ad<-read_rds("area_data.Rds")
```


1. Plot home ownership `perc_homeown` as a function of college education `college_educ` and comment on what you see.

```{r}
gg<-ad%>%
  ggplot(aes(x=college_educ,y=perc_homeown,label=name))+
  geom_point()+
  geom_smooth(method="lm")

  ggplotly(gg)
```



2. Run a regression of home ownership on college education (home ownership is the dependent variable, percent college educated is the independent variable). 


## Training and Testing Data
```{r}
set.seed(35202)

split_data<-ad%>%initial_split(prop=.5)

ad_train<-training(split_data)

ad_test<-testing(split_data)

```


```{r}
homeown_formula<-as.formula("perc_homeown~college_educ")
```




```{r}
lm_fit <- 
  linear_reg() %>% 
  set_engine("lm")%>%
  set_mode("regression")
```


```{r}
lm_results<-
  lm_fit%>%
  fit(homeown_formula,data=ad_train)
```


```{r}
summary(lm_results$fit)
```



3. Summarize the relationship between home ownership and college education in a sentence.

There is a modest, but statistically significant relationship between the percent of the population with a bachelor's degree and the  percent of the  population that own their  own homes. For every one percent increase in the percent of the population with a bachelor's degree, homeownership is predicted to decline by one tenth of a percent (or so). 


4. Calculate a summary of the fit of the above model and comment on what it means.


```{r}
ad_test<-lm_results%>% ## start with the results
  predict(new_data=ad_test)%>% ## create a prediction
  rename(pred1=.pred)%>%  ## rename the prediction
  bind_cols(ad_test) ## add the prediction to the testing dataset
```

## Calculate RMSE
```{r}
rmse_1<-rmse(ad_test,
     truth=perc_homeown,
     estimate=pred1)

rmse_1
```



5. Add the variable for income to the above regression and repeat steps 1-4. 



```{r}
homeown_formula<-as.formula("perc_homeown~college_educ+income_75")
```


```{r}
lm_fit <- 
  linear_reg() %>% 
  set_engine("lm")%>%
  set_mode("regression")
```


```{r}
lm_results<-
  lm_fit%>%
  fit(homeown_formula,data=ad_train)
```


```{r}
summary(lm_results$fit)
```



```{r}
ad_test<-lm_results%>% ## start with the results
  predict(new_data=ad_test)%>% ## create a prediction
  rename(pred2=.pred)%>%  ## rename the prediction
  bind_cols(ad_test) ## add the prediction to the testing dataset
```



## Calculate RMSE
```{r}
rmse_1<-rmse(ad_test,
     truth=perc_homeown,
     estimate=`pred1...2`)

rmse_1
```
