---
title: "Assignment 7"
author: "Doyle"
---

Assignment 7 (alternate)
---
```{r}
library(tidyverse)
library(plotly)
```
For this assignment, I want you to use the Census ACS API to download and plot data. Complete the following steps:

1. Scrape the data on GDP per capita by country from wikipedia here: https://en.wikipedia.org/wiki/List_of_countries_by_GDP_(PPP)_per_capita
Turn this data into a data frame. 

```{r}

gdp_wiki<-"https://en.wikipedia.org/wiki/List_of_countries_by_GDP_(PPP)_per_capita"

gdp_percap<-read_html(gdp_wiki)%>%html_table()

gdp_percap<-gdp_percap[[2]]

gdp_percap<-
  gdp_percap%>%
  select(1,8)%>%
  rename(country=1,gdp_percap=2)%>%
  slice(-1)%>%
  mutate(gdp_percap=parse_number(gdp_percap))%>%
  mutate(country=str_remove(country, fixed("(more)")))%>%
  mutate(country=str_trim(country))


```


2. Download the data on tertiary education in 2019 (first table) by country from wikipedia here:
https://en.wikipedia.org/wiki/List_of_countries_by_tertiary_education_attainment

Turn this data into a data frame.
```{r}

educ_wiki<-"https://en.wikipedia.org/wiki/List_of_countries_by_tertiary_education_attainment"

educ<-read_html(educ_wiki)%>%html_table()

educ<-educ[[1]]

educ<-educ%>%
  select(1,2)%>%
  rename(country=1,educ_level=2)%>%
  slice(-1)%>%
  mutate(educ_level=parse_number(educ_level))

```


3. Join the two data frames you created.

```{r}
combined<-left_join(educ,gdp_percap,by="country")
```


4. Plot gdp per capita (CIA version) as a function of the percent of the population aged 25-64 with a tertiary education. 

```{r}
gg<-combined%>%
  ggplot(aes(x=educ_level,y=gdp_percap,label=country))+
  geom_point()

ggplotly(gg)
```



5. Model gdp per capita (using a linear model) as a function of the percent of the population aged 25-64 with a tertiary education. 

```{r}
mod1<-lm(gdp_percap~educ_level,data=combined)
summary(mod1)
```

