---
title: "Assignment 7"
author: "Doyle"
date: "3/25/2021"
output: html_document
---

Assignment 7
---

For this assignment, I want you to use the Census ACS API to download and plot data. Complete the following steps:

```{r}
library(tidyverse)
library(tidycensus)
```


1. Download data for all of the counties in Georgia on education levels. 

```{r}

# Get your own key and save as my_acs_key.txt
#my_acs_key<-readLines("my_acs_key.txt",warn = FALSE)
#acs_key<-my_acs_key

acs_key<-"b27a265fe0dc7c49bd9281d6bc778637f10685e3"

census_api_key(acs_key,install=FALSE,overwrite =TRUE)

# OR just paste it here.

```



2. Compute the proportion of the population in each county that has a bachelor's degree or above by county.

```{r}
## Educ Characteristics by County for Texas

educ_vars<-get_acs(geography = "county",state="GA",
                    table="B15003",geometry = TRUE)


## Spread, so that each level of education gets its own column
educ_vars<-educ_vars%>%
  select(GEOID,NAME,variable,estimate)%>%
  spread(key=variable,value = estimate)

## rename to be all lower case 
names(educ_vars)<-str_to_lower(names(educ_vars))

## Calculate prop with at least bachelor's for every county
educ_vars<-educ_vars%>%
  mutate(prop_bach=(b15003_022+
                    b15003_023+
                    b15003_024+
                    b15003_025)/b15003_001)

## simplify to just proportion
educ_vars<-educ_vars%>%
  select(geoid,name,prop_bach)
```


3. Download data for all of counties in Georgia for family income. 

4. Compute the proportion of the population in each county that has family income above 75,000. 


```{r}

## Income by County for Georgia

income_vars<-get_acs(geography = "county",state="GA",
                    table="B19001",
                    geometry=TRUE)

## Spread, so that each level of education gets its own column
income_vars<-income_vars%>%
  select(GEOID,NAME,variable,estimate)%>%
  spread(key=variable,value = estimate)

## rename to be all lower case 
names(income_vars)<-str_to_lower(names(income_vars))

## Calculate prop with at least bachelor's for every county
income_vars<-income_vars%>%
  mutate(prop_75p=(b19001_013+
                    b19001_014+
                    b19001_015+
                    b19001_016+
                    b19001_017)/b19001_001)                      

## simplify to just proportion
income_vars<-income_vars%>%
  select(geoid,name,prop_75p)

```


5. Download data for all of the counties in Georgia on health insurance coverage status.
6. Calculate the proportion of the population in each county that does not have health insurance. 



```{r}

v18 <- load_variables(2018, "acs5", cache = TRUE)

```


```{r}

insurance_vars<-get_acs(geography = "county",state="GA",
                    table="B27010",geometry = TRUE)

## Spread, so that each level of education gets its own column
insurance_vars<-insurance_vars%>%
  select(GEOID,NAME,variable,estimate)%>%
  spread(key=variable,value = estimate)

## Calculate prop with at least bachelor's for every county
insurance_vars<-insurance_vars%>%
  mutate(prop_without_health_ins=((B27010_017+
                                  B27010_033+
                                  B27010_050+
                                  B27010_066)/B27010_001))

## rename to be all lower case 
names(insurance_vars)<-str_to_lower(names(insurance_vars))

## simplify to just proportion
insurance_vars<-insurance_vars%>%
  select(geoid,name,prop_without_health_ins)


```




7. Plot the proportion uninsured as a function of education, and then as a function of income. 

```{r}

educ_vars_2<-educ_vars%>%as_tibble()%>%select(geoid,name,prop_bach)

income_vars_2<-income_vars%>%as_tibble()%>%select(geoid,name,prop_75p)

insurance_vars_2<-insurance_vars%>%as_tibble()%>%select(geoid,name,prop_without_health_ins)

combined<-left_join(educ_vars_2,income_vars_2,by=c("geoid","name"))

combined<-left_join(combined,insurance_vars_2,by=c("geoid","name"))
```

```{r}
combined%>%
  ggplot(aes(x=prop_bach,y=prop_without_health_ins))+
  geom_point()
```


```{r}
combined%>%
  ggplot(aes(x=prop_75p,y=prop_without_health_ins))+
  geom_point()
```



8. Model the proportion uninsured as a function of education and income.


```{r}
mod1<-lm(prop_without_health_ins~prop_bach+prop_75p,data=combined)
summary(mod1)
```
