---
title: "In Class Work: Webscraping"
output: html_document  
---




## Complete the following steps

1. Using the `acs` package, download data on mean transportation time ("MEANS OF TRANSPORTATION TO WORK BY TRAVEL TIME TO WORK FOR WORKPLACE GEOGRAPHY") by county for individuals who live in California.  

(you can find table information here: https://www.census.gov/programs-surveys/acs/technical-documentation/table-shells.html)

2. Calculate the proportion of individuals who have commutes of more than one hour.

3. Plot the results by county, ordered from highest proportion to lowest. 

4. Plot the proportion of individuals with commutes of more than an hour as a function of the proportion of the population with a bachelor's degree. 

## Worked example from class


## Download data on owner-occupied housing
```{r}
housing_vars<-get_acs(geography = "county",state="CA",
                    table="B25008")
```

```{r}
housing_vars<-housing_vars%>%
  select(GEOID,NAME,variable,estimate)%>%
  spread(key=variable,value = estimate)
```

```{r}
housing_vars<-housing_vars%>%
  mutate(prop_owner_occupied=B25008_002/B25008_001)
```

```{r}
housing_vars%>%
  ggplot(aes(y=prop_owner_occupied,x=fct_reorder(NAME,prop_owner_occupied)))+
  geom_point()+
  coord_flip()
```

