---
title: "08-assignment"
author: "Doyle"
date: "4/6/2021"
output: html_document
---

Assignment 8
---

"When life gives you lemons, don’t make lemonade. Make life take the lemons back! Get mad!" -Cave Johnson

For this assignment, you'll be using the lemons dataset, which is a subset of the dataset used for a Kaggle competition described here: 
https://www.kaggle.com/c/DontGetKicked/data. Your job is to predict which cars are most likely to be lemons. Please note

Complete the following steps.

```{r}
library(tidyverse)
library(tidymodels)
library(knitr)
```

## Read just the first 100k rows
```{r}
df<-read_csv("training.csv",n_max=1e6)
```

## Recode isbadbuy to be a factor, required for `recipe` command and others. 
```{r}
df<-df%>%
  mutate(isbadbuy_f=fct_recode(as.factor(IsBadBuy),"Yes"="1","No"="0"))
```


1. Calculate the proportion of lemons in the training dataset using the `IsBadBuy` variable. 

```{r}
df%>%
  summarize(mean(IsBadBuy,na.rm=TRUE))
```


2. Calculate the proportion of lemons by Make. 

```{r}
df%>%
  group_by(Make)%>%
    summarize(mean_isbabduy=mean(IsBadBuy,na.rm=TRUE))%>%
    arrange(-mean_isbabduy)%>%
    kable()
```



3. Now, predict the probability of being a lemon using a logistic regression, using covariates of your choosing.  

```{r}

lemon_split<-initial_split(df)

lemon_train<-training(lemon_split)

lemon_test<-testing(lemon_split)

```


```{r}
lemon_formula<-as.formula("isbadbuy_f~
                          VehicleAge+
                          Make+
                          Color+
                          Transmission+
                          VNST+
                          VehBCost+
                          VehOdo")

```

```{r}
lemon_recipe<-recipe(lemon_formula,lemon_train)%>%
  step_dummy(all_nominal(),-all_outcomes())%>%
  step_log(VehBCost,VehOdo)%>%
  step_naomit()%>%
  step_other(Make,threshold = .1)
  
```


```{r}
lemon_model<-
  logistic_reg()%>%
  set_engine("glm")%>%
  set_mode("classification")

```

```{r}
lemon_wf<-workflow()%>%
  add_recipe(lemon_recipe)%>%
  add_model(lemon_model)
```

```{r}
lemon_results<-fit(lemon_wf,lemon_train)
```


```{r}
lemon_results%>%tidy()%>%kable()
```


4. Make predictions from the logit model. Make sure these are probabilities.

```{r}
lemon_results%>%
  predict(lemon_test)%>%
  bind_cols(lemon_test)
```



5. Calculate the accuracy, sensitivity and specificity of your model using a threshold of .5.

```{r}
lemon_results%>%
  predict(lemon_test)%>%
  bind_cols(lemon_test)%>%
   metrics(truth=isbadbuy_f,estimate=.pred_class)
```

```{r}
lemon_results%>%
  predict(lemon_test)%>%
  bind_cols(lemon_test)%>%
  sens(truth=isbadbuy_f,estimate=.pred_class,event_level="second")
```

```{r}
lemon_results%>%
  predict(lemon_test)%>%
  bind_cols(lemon_test)%>%
  spec(truth=isbadbuy_f,estimate=.pred_class,event_level="second")
```




5. Calculate the AUC for the predictions from the ROC based on the logit model. 

```{r}
lemon_results%>%
  predict(lemon_test,type="prob")%>%
  bind_cols(lemon_test)%>%
  roc_auc(truth=isbadbuy_f,estimate=.pred_Yes,event_level="second")

```

```{r}
lemon_results%>%
  predict(lemon_test,type="prob")%>%
  bind_cols(lemon_test)%>%
  threshold_perf(truth=isbadbuy_f,
                 estimate=.pred_Yes,
                 thresholds=.12,metrics=c("sens","spec"))
```




```{r}
th<-lemon_results%>%
  predict(lemon_test,type="prob")%>%
  bind_cols(lemon_test)%>%
   threshold_perf(truth=isbadbuy_f,
                 estimate=.pred_Yes,
                 thresholds=seq(0,1,by=.1),metrics=c("sens","spec"))

ggplot(filter(th,.metric%in%c("sens","spec")),
       aes(x=.threshold,y=.estimate,color=.metric))+
  geom_line()
  

```

```{r}
lemon_mod<-extract_model(lemon_results)

lemon_data<-lemon_recipe%>%
  prep()%>%
  juice()

hypo_data<-
  data_grid(
            data=lemon_data,
            .model=lemon_mod,
            VehicleAge=seq_range(VehicleAge,n=10)
  )%>%
  add_predictions(lemon_mod,type="response")
  
hypo_data%>%
  ggplot(aes(x=VehicleAge,y=pred))+
  geom_smooth()

```


