---
title: "08-assignment"
author: "Doyle"
date: "4/6/2021"
output: html_document
---

Assignment 8
---

"When life gives you lemons, don’t make lemonade. Make life take the lemons back! Get mad!" -Cave Johnson

For this assignment, you'll be using the lemons dataset, which is a subset of the dataset used for a Kaggle competition described here: 
https://www.kaggle.com/c/DontGetKicked/data. Your job is to predict which cars are most likely to be lemons. Please note

Complete the following steps.

```{r}
library(tidyverse)
library(tidymodels)
library(knitr)
```

## Read just the first 100k rows
```{r}
df<-read_csv("training.csv",n_max=1e5)
```

## Recode isbadbuy to be a factor, required for `recipe` command and others. 
```{r}
df<-df%>%
  mutate(isbadbuy_f=fct_recode(as.factor(IsBadBuy),"Yes"="1","No"="0"))
```


1. Calculate the proportion of lemons in the training dataset using the `IsBadBuy` variable. 


2. Calculate the proportion of lemons by Make. 




3. Now, predict the probability of being a lemon using a logistic regression, using covariates of your choosing.  



4. Make predictions from the logit model. Make sure these are probabilities.



5. Calculate the accuracy, sensitivity and specificity of your model using a threshold of .5.




6. Calculate the AUC for the predictions from the ROC based on the logit model. 

