---
title: "In Class Work: Classification"
---

We'll be again working on a Kaggle-style competition to predict who gets pizza. Using the pizza dataset, find the best fit to the data. However, to qualify as a winner, you need to do the following: 

1. Fit a model using logistic regression using the training dataset.


2. Compute the predictions from your model from the testing dataset.

3. Calculate the AUC (from the Receiver Operating Characteristic) for the predictions from your model from the testing dataset. Compare your results to the artice linked below. 



```{r libraries}
library(knitr)
library(tidyverse)
library(modelr)
library(yardstick)
library(tidymodels)
library(probably)
```


```{r}
load("za.RData")
```


```{r}
# Training and testing datasets

za_split<-initial_split(za,prop=.5)

za_train<-training(za_split)

za_test<-testing(za_split)

```



```{r linear_model}
#  Model terms

za_formula<-as.formula("got_pizza_f~
             age+
             karma+
             total_posts+
             raop_posts+
             student+
             grateful+
             pop_request+
             score+
             prev_raop_post+
             words+
             activity")

```


```{r}
za%>%
  ggplot(aes(x=log(activity+1)))+
  geom_density()
```


```{r}
logit_rec<-recipe(za_formula, data=za)%>%
  step_log(total_posts,offset = 1)%>%
  step_log(activity,offset=1)
```



```{r}
logit_mod <- 
  logistic_reg() %>% 
  set_engine("glm")%>%
  set_mode("classification")
```


## Put the workflow together

```{r}
logit_wf<-workflow()%>%
  add_recipe(logit_rec)%>%
  add_model(logit_mod)
```

```{r}
logit_results<-fit(logit_wf,data=za_train)
```

```{r}
logit_results%>%
  tidy()
```

```{r}
logit_final<-last_fit(logit_wf,za_split)

logit_final$.metrics
```

```{r}

```


```{r}

```




4. Find a way to plot the predictions from your model. 

For some ideas, see: http://cs.stanford.edu/~althoff/raop-dataset/altruistic_requests_icwsm.pdf.