---
title: "Assignment 9"
author: "Will Doyle"
---

For this assignment, you'll be using the lemons dataset, which is a subset of the dataset used for a Kaggle competition described here: 
https://www.kaggle.com/c/DontGetKicked/data. 
Complete the following steps:

```{r}
library(tidyverse)
library(knitr)
library(modelr)
```

```{r}
df<-read_csv("training.csv",n_max=1e6)
```


1. Using the lemons dataset, plot the probability of a car being a bad buy by make.

```{r}

df%>%
  mutate(Make=fct_lump_prop(Make,prop=.01,other_level = "Other"))%>%
  group_by(Make)%>%
  summarize(mean_isbadbuy=mean(IsBadBuy,na.rm=TRUE))%>%
  mutate(Make=fct_reorder(Make,mean_isbadbuy))%>%
  ggplot(aes(y=mean_isbadbuy ,x=Make) )+
  geom_col()+
  coord_flip()+
  ylab("Pr(Is Bad Buy)")+
  xlab("")
  
```


2. Create a table that shows the probability of a car being a bad buy by make.

```{r}
df%>%
  mutate(Make=fct_lump_prop(Make,prop=.01,other_level = "Other"))%>%
  group_by(Make)%>%
  summarize(mean_isbadbuy=mean(IsBadBuy,na.rm=TRUE))%>%
  arrange(-mean_isbadbuy)%>%
  mutate(mean_isbadbuy=round(mean_isbadbuy,2))%>%
  rename(`Pr(Bad Buy)`=mean_isbadbuy)%>%
  kable()
```


3. Create a heatmap of the probability of a car being a bad buy by make and vehicle age. 

```{r}
df%>%
  mutate(Make=fct_lump_prop(Make,prop=.01,other_level = "Other"))%>%
  group_by(Make,VehicleAge)%>%
 summarize(mean_isbadbuy=mean(IsBadBuy,na.rm=TRUE))%>%
  rename(`Pr(Bad Buy)`=mean_isbadbuy)%>%
 drop_na()%>%
 filter(VehicleAge>0)%>%  
ggplot(
           aes(y=as.factor(Make),
               x=as.factor(VehicleAge),fill=`Pr(Bad Buy)`))+
 geom_tile()+
 scale_fill_gradient(low="white",high="red")+
  xlab("Vehicle Age in Years")+ylab("")
  
```


4. Create a plot of your choosing that shows the probability of a car being a bad buy by year and make. 

```{r}
df%>%
  mutate(Make=fct_lump_prop(Make,prop=.01,other_level = "Other"))%>%
  group_by(Make,VehYear)%>%
  summarize(mean_isbadbuy=mean(IsBadBuy,na.rm=TRUE))%>%
  mutate(Make=fct_reorder(Make,mean_isbadbuy))%>%
  rename(`Pr(Bad Buy)`=mean_isbadbuy)%>%
  drop_na()%>%
  filter(VehYear!=2010)%>% 
  ggplot(aes(x=VehYear,y=`Pr(Bad Buy)`,color=Make))+
  geom_point()+
  facet_wrap(~Make)+
  theme(legend.position = "none")+xlab("")

```

