---
title: "Assignment 10"
author: "Will Doyle"
output: html_document
---

Complete the following steps:

1. Using the counties dataset (`pd.Rdata`), create a model that predicts median household income (`median_hh_inc`).
```{r}
library(tidyverse)
library(tidymodels)
library(glmnet)
```

```{r}
load("pd.RData")

pd<-pd%>%
  select(median_home_val,median_hh_inc,coll_grad_pc,homeown_rate,per_capita_inc,pop65p,retail_percap)%>%
  mutate_all(.funs=list(as.numeric))
```

```{r}
pd%>%
  ggplot(aes(x=median_hh_inc))+
  geom_density()

```

```{r}
lm_fit <- 
  linear_reg() %>% 
  set_engine("lm")
```

```{r}
lm_formula<-as.formula("median_hh_inc~.")
```

```{r}
lm_rec <- recipe(lm_formula, data = pd) %>%
  step_log(all_outcomes(),offset=1)%>%
  step_zv(all_numeric()) %>% # drop any zero variance
  step_naomit(all_predictors())
```

```{r}
lm_workflow<-workflow()%>%
  add_recipe(lm_rec)%>%
  add_model(lm_fit)
```


2. Provide the results of a 10-fold cross validation of your model. Describe what the results mean in a few clear sentences. Plot the results. 

```{r}
pd_kfold_rs<-vfold_cv(pd,v=10)
```

```{r}
lm_mc_results<-
  fit_resamples(
    lm_workflow,
    pd_kfold_rs, ##resampling plan
    control=control_resamples(save_pred = TRUE)
  )
```


```{r}
lm_mc_results%>%
  collect_metrics()
```

```{r}
lm_mc_results%>%
  unnest(.metrics)%>%
  filter(.metric=="rmse")%>%
  ggplot(aes(x=.estimate))+
  geom_density()
```


3. Provide the results of a 1000 repetition monte carlo validation with 10 percent (`prop=.9`) leave out rate for the random partition. Describe what the results mean in a few clear sentences. Plot the results. 

```{r}
pd_mc_rs<-mc_cv(pd,times = 100,prop = .9) ##1000 is usual minimum
```


## Fit Monte Carlo Resampling
```{r}
lm_mc_results<-
  fit_resamples(
    lm_workflow,
    pd_mc_rs, ##resampling plan
    control=control_resamples(save_pred = TRUE)
  )
```



```{r}
lm_mc_results%>%
  collect_metrics()
```

```{r}
lm_mc_results%>%
  unnest(.metrics)%>%
  filter(.metric=="rmse")%>%
  ggplot(aes(x=.estimate))+
  geom_density()
```

```{r}
df_split<-initial_split(df,prop=.8)
```


```{r}
last<-lm_workflow%>%last_fit()
```



