---
title: "Cross Validation Logistic (Minimal)"
author: "Will Doyle"
date: "8/11/2021"
output: html_document
---

```{r}
library(tidyverse)
library(tidymodels)
library(glmnet)
library(modelr)
library(modelsummary)
```

```{r}
load("za.RData")

za<-za%>%
  drop_na()%>%
  mutate(got_pizza_f=fct_relevel(got_pizza_f,"Yes","No"))%>%
  select(-got_pizza)%>%
  mutate(student_f=as.factor(student))
```

## Set formula for classification

I'll use a model similar to the one we used in our lesson to predict whether or not someone received a pizza.

```{r}
#  Model terms
za_formula<-as.formula("got_pizza_f~
             age+
             karma+
             total_posts+
             raop_posts+
             student+
             grateful+
             pop_request+
             score")
```

```{r}
logit_rec <- recipe(za_formula, data = za) %>%
  step_zv(all_numeric()) %>% # drop any zero variance
  step_dummy(all_nominal(),-all_outcomes())%>%
  step_naomit(all_predictors(),all_outcomes()) 
```

```{r}
logit_fit<-
  logistic_reg(mode="classification")%>%
  set_engine("glm")
```

## Creat Workflow for Logit Model

We can combine the model and recipe into our workflow.

```{r}
logit_wf<-workflow()%>%
  add_recipe(logit_rec)%>%
  add_model(logit_fit)
```

## Specify the MC setup

```{r}
logit_mc_rs<-mc_cv(za,times=10)
```

## Fit Logit Model to Resampleld Data

And now we can fit the model to the resamples. Note that in the metric I ask for our key measures of roc_auc, accuracy, sensitivity and specificity.

```{r}
logit_mc <- 
  fit_resamples(
    logit_wf,
    logit_mc_rs,
    metrics = metric_set(roc_auc, sens, spec, accuracy)
  )
```

## Collect Metrics from Logit model

```{r}
mymetrics<- logit_mc%>%
  collect_metrics()
```

The average AUC from the cross validation is `r round(mymetrics$mean[2], 2) `

```{r}
karma_mean<-za%>%summarize(mean(karma,na.rm=TRUE))
```

The average karma is `r prettyNum(karma_mean[1],big.mark=",",digits=0)` 

## Plot distribution of AUC

Above we plotted the distribution of rmse for the repeated fitting of the linear model. As this is a model for classification, we'll use the AUC instead.

```{r}
logit_mc%>%
  unnest(.metrics)%>%
  filter(.metric=="roc_auc")%>%
  ggplot(aes(x=.estimate))+
  geom_density()
```

```{r}
final_fit<-fit(logit_wf,za)

final_estimates<-extract_model(final_fit)

modelsummary(final_estimates,statistic = "p.value")

```
